Sketch of DP - Bayesian Inference

### 2018-07-14 main-sketch.tex
update abstracts

\begin{abstract}

  Bayesian inference is a statistical method which allows to derive
  a \emph{posterior} distribution over a parameter, 
  starting from a \emph{prior} distribution and observed data.
  Many works have focused on making this
  process differentially private adding noise on the parameters
  representing the distributions\cite{zhang2016differential}.
  % Also,  the sensitivity 
  % was computed w.r.t. a numeric norm over the space of the numeric parameters
  % characterizing the output distribution.
  Also, the accuracy was measured
  using metrics on the space of the numeric parameters representing the
  posterior distribution, e.g. $\ell_1$-norm \cite{foulds2016theory}.

  We designed a new mechanism for differentially private Bayesian inference
  where the noise is proportional to a smooth sensitivity computed w.r.t a metric
  on probability distributions; we also measured the accuracy of the process
  by using a metric over probability measures.
  We compared the accuracy of this approach with the one based on $\ell_1$-norms.
  Experimental results show that in some situations the former outperforms the latter.

>>>>

\begin{abstract}
Bayesian inference is a statistical method which allows to derive a \emph{posterior} distribution over a parameter, starting from a \emph{prior} distribution and observed data. Even the posterior sampling is differentially private itself under some conditions \cite{wang2015privacy,dimitrakakis2014robust}, it can still leak sensitive information of observed data when we release the posterior distribution directly rather than just a sample from it. Many works have focused on making this process differentially private by adding noise on the parameters representing the distributions.
  % Also,  the sensitivity 
  % was computed w.r.t. a numeric norm over the space of the numeric parameters
  % characterizing the output distribution.
Also, the accuracy was measured using metrics on the space of the numeric parameters representing the posterior distribution, e.g. $\ell_1$-norm \cite{foulds2016theory, zhang2016differential}.

We designed a new mechanism for differentially private Bayesian inference where the noise is proportional to a smooth sensitivity computed w.r.t a metric on probability distributions; we also measured the accuracy of the process by using a metric over probability measures. We protect the whole Bayesian inference process with the posterior distribution. We compared the accuracy of this approach with the one based on $\ell_1$-norms. Experimental results show that in some situations the former outperforms the latter.
